\section{Introduction}

Knowing-how logics study an agent's ability to achieve goals by suitable action. This makes them particularly relevant to artificial intelligence, especially to planning, where the main question is whether a desired objective can be guaranteed by some plan.\par

The simplest knowing-how logic, $\mathcal{L}_{Kh}$, was first introduced in \cite{Wang2015}. This logic captures an agent's ability to guarantee the achievement of a goal under a given condition. In this sense, the notion is somewhat idealized: even if an agent manages to achieve something under a condition, this does not necessarily mean that the agent genuinely knows how to do it. For example, winning a lottery does not imply knowing how to win it. In such cases, uncertainty becomes essential.\par

To address this, one may move to the uncertainty-based knowing-how logic $\mathcal{L}^U_{Kh}$ \cite{Areces2021}, which supports multi-agent reasoning. In this logic, an agent may have several indistinguishable plans for achieving the same purpose. This adds an epistemic feature to the basic knowing-how logic: plans are grouped into equivalence classes representing the agent's uncertainty about which plan is being followed. Finally, the uncertainty-based logic with regularity constraints $reg\text{-}\mathcal{L}^U_{Kh}$ connects this approach with formal language theory by representing such equivalence classes using finite automata.\par

In this work, we present \textsf{KHora}, a model-checking tool for both $\mathcal{L}_{Kh}$ and $reg\text{-}\mathcal{L}^U_{Kh}$ in $\textsf{Haskell}$. For $\mathcal{L}_{Kh}$, the tool implements an explicit bounded search over plans; for $reg\text{-}\mathcal{L}^U_{Kh}$, it realises the algorithms of \cite{Demri2023} in an executable setting. In addition to the core model checkers, \textsf{KHora} includes parsers for both logics, random generators for models and formulas, a collection of tests based on \texttt{QuickCheck} and \texttt{HSpec}, and a lightweight web interface that visualizes the generation of formulas and models.\par

The repository is available on GitHub at:\\
\url{https://github.com/Knowing-How-Logics/haskell-knowing-how-logics}.